Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
update density plot Draft1Rmd.Rmd

url <- c("https://raw.githubusercontent.com/mardimardimardi/ECNS_460_TopicData/main/Data/Cleaned%20Data/CleanedStateHealthRankings/MergedAllCountyRanks.csv")
# Read csv
data <- read.csv(url)

@@

>>>>

# Replace 'your/path/to/directory' with the actual path to your desired working directory
setwd("your/path/to/directory")

# Change file path name to your directory
file_path <- c("project/cleaned/MergedAllCountyRanks2.csv")
# Read csv
data <- read.csv(file_path)

@@

``` {r warnings = FALSE}
# Show deaths per-capita for each state
data2 <- health_ranking |>
  mutate(od_deaths_percapita = combined_overdose_deaths / population)

# All states and overdose death per-capita for years 2016, 2020, 2023
data2 |>
  filter(year %in% c(2016, 2018, 2020, 2023) & !is.na(od_deaths_percapita)) |>
  ggplot(aes(od_deaths_percapita, y = after_stat(count), fill = state)) +
  scale_x_continuous(
    trans = "log10",
    labels = scales::label_number(scale = 1e6, suffix = "M")  # Adjust scale based on your data
  ) +
  geom_density(alpha = 0.3, position = "stack", linetype = "solid", size = 1) +  # Use linewidth instead of size
  facet_grid(year ~ .) +
  labs(
    title = "Density Plot of Overdose Deaths Per Capita by State",
    x = "Overdose Deaths Per Capita",
    y = "Count of Overdose Deaths",
    fill = "State"
  ) +
  theme_minimal()  # Customize the theme if needed
